Volatility and the Buyback Anomaly

### 2016-04-25 bb_issuers_new.Rnw
clean up

%%Blind title page
%\begin{titlepage}
%\begin{center}
%  \centering
%\vskip 60pt
%\LARGE Share Buyback and Equity Issue Anomalies Revisited \par
%\vskip 1.5em
%\normalsize  \today
%\noindent \\ 
%\begin{abstract}
%\noindent We re-examine the behavior of stock returns after net issue  announcements using the five-factor model proposed by Fama and French (2015a). We confirm their findings that the equity issue anomaly disappears  with the five-factor model, but the buyback anomaly does not. Buyback announcements by firms  with high pre-announcement (idiosyncratic) volatility  are followed by higher long-term abnormal returns. This is inconsistent with the widely documented low volatility anomaly, but consistent with Stambaugh, Yu, and Yuan (2015) who find a positive relation between stock returns and idiosyncratic volatility for undervalued stocks.
%\end{abstract}
%\vspace{2cm}
%\end{center}
%\medskip
%\noindent \textit{JEL classification}: G35
%\medskip
%\noindent \textit{Keywords}: Share Buybacks, Seasoned Equity Offerings
%\end{titlepage}

@@

%Figure~\ref{fig:pastall} summarizes the IRATS results in more detail by showing the cumulative abnormal returns during the 6 month pre and 48 month post event period, using the five-factor model. Results are shown for the total sample of buybacks and equity issues, as well as for high and low U-index buyback samples.

@@

%Table~\ref{tbl:BBISSexitAfter} shows the long run excess returns after the announcement of an equity issue for two samples. The first sample (After a Buyback) shows the excess returns for issues for which in the previous 48 months the firm announced a buyback.  The second sample (No Prior Buyback) shows the excess returns for all other issue announcements.  The fact that excess returns are not significantly different from zero for the post-buyback issuers agrees with the intuition of Figure~\ref{fig:BBISSexit}: exiting when there is a subsequent equity issue is a better strategy for the long-term buyback investor.

@@

We report the returns (unhedged strategy) and excess returns (hedged strategy) of such a portfolio strategy for different holding months $N$ = 1, 3, 6, 12, 24, 36, 48 in Figure~\ref{fig:ReturnsBB}.\footnote{Results for other holding periods, as in Figure~\ref{fig:ReturnsBB}, are available upon request.} The basic conclusion is that the shorter the investment horizon the larger the excess returns. Specifically, at the end of \Sexpr{lastyear} the cumulative excess returns from the 1 month, 6 month, 12 month, 24 month, 36 month and 48 month holding periods are respectively equal to \Sexpr{round(tail(months1,1),1)}$\%$, \Sexpr{round(tail(months3,1),1)}$\%$, \Sexpr{round(tail(months6,1),1)}$\%$, \Sexpr{round(tail(months12,1),1)}$\%$, \Sexpr{round(tail(months24,1),1)}$\%$, \Sexpr{round(tail(months36,1),1)}$\%$ and \Sexpr{round(tail(months48,1),1)}$\%$. This is not surprising as the Calendar Time results in Table~\ref{tbl:priorBuybacks} show that the monthly excess returns decline when the investment horizon becomes longer. However, Figure~\ref{fig:ReturnsBB} allows us to verify that the excess returns are not simply the result of outperformance during a particular time period. %Table~\ref{tbl:allhedgedBB} shows the monthly and yearly returns of this five-factors hedged strategy for N=12.  The table shows that in \Sexpr{sum(tmp[,13] > 0)} of \Sexpr{sum(tmp[,13] != 0)} years the excess returns are positive, with a large \Sexpr{round(max(tmp[,13]),1)}$\%$ excess return in  \Sexpr{rownames(tmp)[which.max(tmp[,13])]}. In only one year (\Sexpr{rownames(tmp)[which.min(tmp[,13])]}) the strategy generates an abnormal loss larger than \Sexpr{round(abs(sort(tmp[,13])[2]),1)}$\%$.

%\subsection{Robustness across Sectors}
%\label{sec:AllIndustries}

%<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
%tmp = Reduce(cbind,lapply(1:length(industry_BB), function(i) industry_BB[[i]][,1:3] ))
%@

%Figure~\ref{fig:industryeventsBB} shows the number of buyback events per industry in our sample. The software and semiconductor industries are the most active repurchasers. They also tend to be the most volatile industries, industries where disagreement about fundamental value is large - as we report later in Table \ref{tbl:industriesR2Vol}. Table~\ref{tbl:IndustriesBB} shows the IRATS cumulative abnormal returns and Table~\ref{tbl:IndustriesBB_cal} the Calendar Time method monthly average abnormal returns when we remove one industry at the time, for the top most frequent buyback industries (those for which there are at least \Sexpr{min_industry_sampleBB} events in our sample).  Note from Table~\ref{tbl:priorBuybacks} that, after 48 months, the cumulative abnormal returns for the whole sample (using IRATS) is \Sexpr{round(IRATS_table_all_bb["+48","CAR 5F"],2)}$\%$ and the monthly average excess return (Calendar Time) is \Sexpr{round(CAL_table_all_bb["+48","CAL 5F"],2)}$\%$.  So the larger the difference between these numbers and the corresponding numbers for the industry indicated in Tables~\ref{tbl:IndustriesBB} and \ref{tbl:IndustriesBB_cal}, the larger the excess returns in the industry removed. For example, using IRATS, deleting the software industry lowers the CAR from \Sexpr{round(IRATS_table_all_bb["+48","CAR 5F"],2)}$\%$ to \Sexpr{round(tmp["+48", 3*(which(names(industry_BB) == "Software")-1)+1],2)}$\%$, a \Sexpr{round(IRATS_table_all_bb["+48","CAR 5F"] - tmp["+48", 3*(which(names(industry_BB) == "Software")-1)+1],2)}$\%$ decline. This is the largest decline in Table~\ref{tbl:IndustriesBB}, indicating that buybacks in the software industry are followed by the largest excess returns. However, deleting Retail, Insurance, Machinery, Meals and especially Chemical stocks improves the excess returns.  Of course, these differences could be explained by differences in U-index levels or other indicators of the likelihood of misvaluation, a topic we turn to next.

@@

%The finding that $1-R^2$ and idiosyncratic volatility (IVOL in \citep{Ang2006}, measured as the standard deviation of the residuals of the factor model regression) are positively related to future excess returns is inconsistent with \cite{Ang2006} who find a negative relation between IVOL and expected returns. However, \cite{Stambaugh2015} argue that the relationship between IVOL and returns becomes positive for undervalued stocks. Their argument is that IVOL represents risk that deters arbitrage and therefore creates mispricing. Using a proxy for mispricing based on 11 anomalies they find indeed a positive relation between IVOL and future returns for undervalued stocks. Their most under-priced high IVOL stocks earn monthly excess returns (relative to the Fama-French three-factor model) of 0.56$\%$ per month which is quite similar to the \Sexpr{R2_IRATStableBB_cal["+48","High Idiosync.: CAL"]}$\%$ per month reported in our Table~\ref{tbl:IdiosyncraticunderBB} Panel B (using the five-factor model).  So our results are also consistent with the \cite{Stambaugh2015} interpretation.

@@

Figure~\ref{fig:Eundervaluationindex} shows the distribution of the EU-index. The index has a symmetric distribution with a mean of \Sexpr{round(mean(EUindex_bb),2)}. Table~\ref{tbl:EUrelations} shows how the EU-index relates to a number of firm characteristics. Firm leverage, based on data the year before announcement, is defined as the ratio $debt/(debt+equity)$.\footnote{We use the definitions from \url{http://www.ivo-welch.info/professional/leverage.placebo/}{Ivo Welch's website} following  \url{http://www.ivo-welch.info/professional/leverage.placebo/r-sourcecode/mksane.R}. Debt is the sum of the Compustat variables $dlc+ dltt$, where $dlc$ is ``Debt in Current Liabilities'' and $dltt$ is ``Long Term Debt - Total''. Equity is the Compustat variable $seq$ which is ``Total Parent Stockholders' Equity''. We use the most recent data pre-announce, and make the winsorization and other adjustments as in the websites above. Note that we followed the same steps as in these websites to handle negative book value of equity (in the BE/ME calculations) and any other Compustat data issues.} 
%``Missed (beat) EPS'' measures the percentage of firms in the specific EU index category that missed (beat) the last EPS consensus analyst forecast before the buyback announcement. 
``ISS later'' measures the percentage of firms that announced an equity issue within 48 months after the buyback announcement. Next, we measure the percentage of buybacks financed with cash (CASH) when the data is available\footnote{As this SDC data was not available for many events, we did not consider the in the U-index calculation.} (this data was available only for \Sexpr{sum(!(BUYBACK_DATA$DATASET$SDC$Source...of..Funds..Code == ""))} of the events) and whether the reported purpose (available only for \Sexpr{sum(!(BUYBACK_DATA$DATASET$SDC$Purpose.Code == ""))} events) included the term ``Undervalued'', or ``Enhance Shareholder Value'' or ``stock option plan''.

@@

%Finally, Table~\ref{tbl:EUhedgedBB}, like Table~\ref{tbl:allhedgedBB}, shows the monthly and yearly returns of a five-factors hedged strategy investing only in the high EU-index repurchase events.  The table shows the robustness of the abnormal returns over time. Specifically, in \Sexpr{sum(tmp[,13] > 0)} out of the \Sexpr{sum(tmp[,13] != 0)} years the hedged strategy generates positive excess returns. As in Table~\ref{tbl:allhedgedBB},  \Sexpr{rownames(tmp)[which.min(tmp1[,13])]} has a large a loss of \Sexpr{tmp[which.min(tmp1[,13]),13]}$\%$ and the best year is \Sexpr{rownames(tmp)[which.max(tmp[,13])]} with an impressive \Sexpr{tmp[which.max(tmp[,13]),13]}$\%$.

@@

if (0){
  colnames(ISS_for_BB_Abn_table)[1]<- "Post-buyback SEOs"
  colnames(ISS_for_BB_Abn_table)[4]<- "Other SEOs"
  printLatexTable(ISS_for_BB_Abn_table[c("-6","+1", "+3", "+6","+24","+48","Observations"),],
                  label  = "tbl:BBISSexitAfter",
                  columns= c("After a Buyback","No Prior Buyback"),
                  title  ="Issue announcements with and without a prior buyback",
                  caption = "The table presents the long-run abnormal returns (CAR) for firms after issue announcements for events with and without a prior buyback announcement within 48 months. We report the monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples. The following regression is run each event month~$j$:
\\begin{eqnarray*}
(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
\\end{eqnarray*}
where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement. $R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively. ${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively. The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms. The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors.",

lastSpecial=T,
titleontop = T
  )
}
@

@@

%\clearpage
<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
if (0){
  printLatexTable2(
    Exit_on_BB_Abn_table[reported_times,],
    Exit_on_BB_Abn_table_cal[reported_times,],
    columns = c("No Buyback","Buyback"),
    title="SEOs with and without subsequent buyback",
    title1 = "Panel A: IRATs Cumulative Abnormal Returns",
    title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
    caption="The table presents the long-run abnormal returns for firms after issue announcements with and without a subsequent buyback announcement on the full sample for different periods in time. Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples. The following regression is run each event month~$j$:
\\begin{eqnarray*}
(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
\\end{eqnarray*}
where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement. $R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively. ${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively. The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms. The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors. Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model. In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio. A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables. The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",

label = "tbl:ISSBBexit",
bigtitleontop=T,
titleontop=T,
scale=1,
lastSpecial=T,
dorotate=F
  )

  printLatexTable(BB_for_ISS_Abn_table[c("-6","+1", "+3", "+6","+24","+48","Observations"),],
                  label  = "tbl:ISSBBexitAfter",
                  columns= c("post-Issue Buybacks: CAR","Other Buybacks: CAR"),
                  title  ="Long-run IRATS abnormal return of only the buybacks that are announced within 48 months after an SEO announcement versus the remaining buyback events.",lastSpecial=T)
}
@

@@

label = "tbl:PastFindingsTimeBB",
bigtitleontop=T,
titleontop=T,
metric1 = "CAR", metric2 = "AR",
scale=1,
lastSpecial=T,
dorotate=T
)

if (0){
  tmp = ISStable_time[reported_times,c(4,5,6,10,11,12,16,17,18,22,23,24)]
  colnames(tmp) <- c("1985-1990: CAR","t-stat","p-value","1991-2000: CAR","t-stat","p-value","2001-2015: CAR","t-stat","p-value","2008-2015: CAR","t-stat","p-value")
  tmp2 = ISStable_time_cal[reported_times,c(4,5,6,10,11,12,16,17,18,22,23,24)]
  colnames(tmp2) <- c("1985-1990: CAL","t-stat","p-value","1991-2000: CAL","t-stat","p-value","2001-2015: CAL","t-stat","p-value","2008-2015: CAL","t-stat","p-value")

  printLatexTable2(
    tmp,
    tmp2,
    columns= c("1985-1990","1991-2000","2001-2015","2008-2015"),
    title="SEOs returns over different time periods",
    title1 = "Panel A: IRATs Cumulative Abnormal Returns",
    title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
    caption="Long-run IRATS cumulative (Panel~A) and Calendar method monthly (Panel~B) abnormal return after issue announcements for different time periods.",
    label = "tbl:PastFindingsTimeISS",
    bigtitleontop=T,
    titleontop=T,
    scale=1,
    lastSpecial=T,
    dorotate=T
  )
}

@@

if (0){
  paste(printLatexTable(BB_cal_table_undertime[reported_times,1:12],
                        columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),
                        rowcolumn="1985-1990",
                        title="Calendar Method abnormal returns after open market repurchase announcements  for under and over valued companies over different time periods.",
                        label="tbl:PastFindingsTimeUnderBBcal",
                        scale = 0.8,close=F,lastSpecial=T
  ),
  printLatexTable(BB_cal_table_undertime[reported_times,13:24],open=F,close=F,rowcolumn="1991-2000",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
  printLatexTable(BB_cal_table_undertime[reported_times,25:36],open=F,close=F,rowcolumn="2001-2015",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
  printLatexTable(BB_cal_table_undertime[reported_times,37:48],open=F,rowcolumn="2008-2015",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T), sep="\n")

}
if (0){
  paste(printLatexTable(ISStable_undertime[reported_times,1:12],
                        columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),
                        rowcolumn="1985-1990",
                        title="Long-run IRATS abnormal returns after issue announcements  for under and over valued companies over different time periods.",
                        label="tbl:PastFindingsTimeUnderISS",
                        scale = 0.9,close=F,lastSpecial=T
  ),
  printLatexTable(ISStable_undertime[reported_times,13:24],open=F,close=F,rowcolumn="1991-2000",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
  printLatexTable(ISStable_undertime[reported_times,25:36],open=F,close=F,rowcolumn="2001-2015",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
  printLatexTable(ISStable_undertime[reported_times,37:48],open=F,rowcolumn="2008-2015",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T), sep="\n")

  paste(printLatexTable(ISS_cal_table_undertime[reported_times,1:12],
                        columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),
                        rowcolumn="1985-1990",
                        title="Calendar Method abnormal returns after issue announcements  for under and over valued companies over different time periods.",
                        label="tbl:PastFindingsTimeUnderISScal",
                        scale = 0.9,close=F,lastSpecial=T
  ),
  printLatexTable(ISS_cal_table_undertime[reported_times,13:24],open=F,close=F,rowcolumn="1991-2000",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
  printLatexTable(ISS_cal_table_undertime[reported_times,25:36],open=F,close=F,rowcolumn="2001-2015",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T),
  printLatexTable(ISS_cal_table_undertime[reported_times,37:48],open=F,rowcolumn="2008-2015",columns = c("Under 3FF","Over 3FF","Under 5FF","Over 5FF"),scale = 0.9,lastSpecial=T), sep="\n")
}
@

@@

<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
tmp = Reduce(cbind,lapply(1:length(industry_BB), function(i) industry_BB[[i]][,1:3] ))
tmp_cal = Reduce(cbind,lapply(1:length(industry_BB), function(i) industry_BB[[i]][,4:6] ))

if (0){
  printLatexTable2(
    tmp[reported_times,1:(3*6)],
    tmp[reported_times,(3*6+1):36],
    columns= names(industry_BB)[1:6],
    columns2= names(industry_BB)[7:12],
    title="Buyback IRATS Abnormal Returns: Industry Robustness",
    #title1 = "",
    #title2 = "",
    caption=paste("The table presents the long-run abnormal returns for firms after repurchase announcements after removing each of the industries indicated from the sample. We report the monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples. The following regression is run each event month~$j$:
\\begin{eqnarray*}
(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
\\end{eqnarray*}
where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement. $R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively. ${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively. The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms. The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors. The 48 month abnormal return for the full sample is equal to ",round(IRATS_table_all_bb["+48","CAR 5F"],2),"$\\%$, other values are reported in Table~\\ref{tbl:priorBuybacks}.",sep=""),

label = "tbl:IndustriesBB",
bigtitleontop=T,
metric1 = "CAR", metric2 = "CAR",
#titleontop=T,
scale=1,
lastSpecial=T,
dorotate=T
  )

  printLatexTable2(
    tmp_cal[reported_times,1:(3*6)],
    tmp_cal[reported_times,(3*6+1):36],
    columns= names(industry_BB)[1:6],
    columns2= names(industry_BB)[7:12],
    title="Buyback Calendar Method Abnormal Returns: Industry Robustness",
    #title1 = "",
    #title2 = "",
    caption=paste("The table presents the long-run calendar method abnormal returns for firms after repurchase announcements after removing each of the industries indicated from the sample.  Specifically, we report the monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model. In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio. A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors (the difference between the risk-free rate and the return on the equally weighted CRSP index, the monthly return on the size, book-to-market factor, profitability factor and investment factor in month) as the independent variables. The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test. The 48 month abnormal return for the full sample is equal to ",round(CAL_table_all_bb["+48","CAL 5F"],2),"$\\%$, other values are reported in Table~\\ref{tbl:priorBuybacks}.",sep=""),
    label = "tbl:IndustriesBB_cal",
    bigtitleontop=T,
    metric1 = "AR", metric2 = "AR",
    #titleontop=T,
    scale=1,
    lastSpecial=T,
    dorotate=T
  )

}
@

<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
if (0){
  latex_render_data_frame(
    pnl_matrix(remove_initialization_time(BUYBACK_DATA$long_all12mshort_risk_factors,min_date=FirstTrade)), 
    title = "Monthly and Yearly Five Factor Abnormal Rerurns of a strategy investing in all buybacks",
    caption="Monthly and yearly five-factor rolling hedged abnormal returns of an equally weighted (with monthly rebalancing) portfolio of all buybacks. The holding period for each buyback is 12 months per event.",
    label="tbl:allhedgedBB", 
    columns=NULL,
    bigtitleontop = T,
    show_rownames=TRUE,
    scale = 0.9,
    digits=1,
    lastSpecial=F,dorotate=F
  )
}
@

@@

#\\textit{Missed (Beat) EPS} measures the percentage of firms in the specific EU index category that missed (beat) the last EPS consensus analyst forecast before the buyback announcement. 
EU_relations <- EU_relations[-which(rownames(EU_relations) %in% c("Missed EPS","Beat EPS")),]

rownames(EU_relations)[1] <- "Low Leverage"
rownames(EU_relations)[2] <- "High Leverage"
latex_render_data_frame(
  round(EU_relations,1), 
  title = "EU relations with Firm Characteristics",
  caption="Firm characteristics for each of the 7 EU-index samples. Percentages indicated for all but the last 3 rows, and averages for the last 3 rows. We consider firm \\textit{leverage}, based on data the year before announcement, defined as the ratio $debt/(debt+equity)$. \\textit{ISS later} measures the percentage of firms that announced an equity issue within 48 months after the buyback announcement. Next, we measure the percentage of buybacks financed with cash (\\textit{CASH}) when the data is available and whether the reported purpose included the term \\textit{Undervalued},  \\textit{Enhance Shareholder Value} or \\textit{stock option plan}. Market Cap. is in millions, BE/ME Score is from 1, for firms below the $4^{th}$ Fama-French BE/ME breakpoint, to 5 for firms above the $16^{th}$. Percentage Shares is the percentage shares authorized at announcement.",
  label = "tbl:EUrelations",
  columns=NULL,
  bigtitleontop = T,
  show_rownames=TRUE,
  scale = 1,
  digits=1,
  lastSpecial=F,dorotate=F
)
@

@@

<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
if (0){
  latex_render_data_frame(
    pnl_matrix(remove_initialization_time(High_EU_BB_Hedged,min_date=FirstTrade)), 
    title = "Monthly and Yearly Five Factor Abnormal Rerurns of a strategy investing in all high EU-index buybacks",
    caption="Monthly and yearly  five-factor rolling hedged abnormal returns of an equally weighted (with monthly rebalancing) portfolio of all high EU-index buybacks only. Holding period for each buyback is 12 months per event.",
    label="tbl:EUhedgedBB", 
    columns=NULL,
    bigtitleontop = T,
    show_rownames=TRUE,
    scale = 0.9,
    digits=1,
    lastSpecial=F,dorotate=F
  )
}
@

@@

%\begin{figure}[H]
%\centering
<< fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
if (0){
  par(mfrow=c(2,2), mar=c(2.3,4,2.3,4))

  IRATS_table_all_bb_plot = IRATS_table_all_bb
  IRATS_table_all_bb_plot[rownames(IRATS_table_all_bb_plot) %in% as.character((-6):(-1)),c("CAR 3F","CAR 5F")] <- -IRATS_table_all_bb_plot[rownames(IRATS_table_all_bb_plot) %in% as.character((-6):(-1)),c("CAR 3F","CAR 5F")] 
  IRATS_table_all_iss_plot = IRATS_table_all_iss
  IRATS_table_all_iss_plot[rownames(IRATS_table_all_iss_plot) %in% as.character((-6):(-1)),c("CAR 3F","CAR 5F")] <- -IRATS_table_all_iss_plot[rownames(IRATS_table_all_iss_plot) %in% as.character((-6):(-1)),c("CAR 3F","CAR 5F")] 
  IRATS_table_all_bb_undervaluation_plot = IRATS_table_all_bb_undervaluation
  IRATS_table_all_bb_undervaluation_plot[rownames(IRATS_table_all_bb_undervaluation_plot) %in% as.character((-6):(-1)),c("U:CAR3F","O:CAR3F", "U:CAR5F","O:CAR5F")] <- -IRATS_table_all_bb_undervaluation_plot[rownames(IRATS_table_all_bb_undervaluation_plot) %in% as.character((-6):(-1)),c("U:CAR3F","O:CAR3F", "U:CAR5F","O:CAR5F")] 
  #IRATS_table_all_iss_undervaluation_plot = IRATS_table_all_iss_undervaluation
  #IRATS_table_all_iss_undervaluation_plot[rownames(IRATS_table_all_iss_undervaluation_plot) %in% as.character((-6):(-1)),c("U:CAR3F","O:CAR3F", "U:CAR5F","O:CAR5F")] <- -IRATS_table_all_iss_undervaluation_plot[rownames(IRATS_table_all_iss_undervaluation_plot) %in% as.character((-6):(-1)),c("U:CAR3F","O:CAR3F", "U:CAR5F","O:CAR5F")]

  ylimit = c(min(
    #IRATS_table_all_bb_plot[reported_times_plots,"CAR 3F"], 
    IRATS_table_all_bb_plot[reported_times_plots,"CAR 5F"], 
    #IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"U:CAR3F"], 
    #IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"O:CAR3F"], 
    IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"U:CAR5F"], 
    IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"O:CAR5F"]), 
    max(
      #IRATS_table_all_bb_plot[reported_times_plots,"CAR 3F"], 
      IRATS_table_all_bb_plot[reported_times_plots,"CAR 5F"], 
      #IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"U:CAR3F"], 
      #IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"O:CAR3F"], 
      IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"U:CAR5F"], 
      IRATS_table_all_bb_undervaluation_plot[reported_times_plots,"O:CAR5F"])
  )

  plot(IRATS_table_all_bb_plot[reported_times_plots,"CAR 5F"], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="A. Buybacks - All", lwd=1.4)
  axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=1,las=3)
  axis(2,cex.axis=1.1)
  #lines(IRATS_table_all_bb_plot[reported_times_plots,"CAR 5F"],  lty = 2,lwd=1.4)
  abline(v=which(reported_times_plots == "0"), lwd=0.5)
  abline(h=0, lwd=0.5)

>>>>

@@

@@

@@

We report the returns (unhedged strategy) and excess returns (hedged strategy) of such a portfolio strategy for different holding months $N$ = 1, 3, 6, 12, 24, 36, 48 in Figure~\ref{fig:ReturnsBB}.\footnote{Results for other holding periods, as in Figure~\ref{fig:ReturnsBB}, are available upon request.} The basic conclusion is that the shorter the investment horizon the larger the excess returns. Specifically, at the end of \Sexpr{lastyear} the cumulative excess returns from the 1 month, 6 month, 12 month, 24 month, 36 month and 48 month holding periods are respectively equal to \Sexpr{round(tail(months1,1),1)}$\%$, \Sexpr{round(tail(months3,1),1)}$\%$, \Sexpr{round(tail(months6,1),1)}$\%$, \Sexpr{round(tail(months12,1),1)}$\%$, \Sexpr{round(tail(months24,1),1)}$\%$, \Sexpr{round(tail(months36,1),1)}$\%$ and \Sexpr{round(tail(months48,1),1)}$\%$. This is not surprising as the Calendar Time results in Table~\ref{tbl:priorBuybacks} show that the monthly excess returns decline when the investment horizon becomes longer. However, Figure~\ref{fig:ReturnsBB} allows us to verify that the excess returns are not simply the result of outperformance during a particular time period.

@@

@@

Figure~\ref{fig:Eundervaluationindex} shows the distribution of the EU-index. The index has a symmetric distribution with a mean of \Sexpr{round(mean(EUindex_bb),2)}. Table~\ref{tbl:EUrelations} shows how the EU-index relates to a number of firm characteristics. Firm leverage, based on data the year before announcement, is defined as the ratio $debt/(debt+equity)$.\footnote{We use the definitions from \url{http://www.ivo-welch.info/professional/leverage.placebo/}{Ivo Welch's website} following  \url{http://www.ivo-welch.info/professional/leverage.placebo/r-sourcecode/mksane.R}. Debt is the sum of the Compustat variables $dlc+ dltt$, where $dlc$ is ``Debt in Current Liabilities'' and $dltt$ is ``Long Term Debt - Total''. Equity is the Compustat variable $seq$ which is ``Total Parent Stockholders' Equity''. We use the most recent data pre-announce, and make the winsorization and other adjustments as in the websites above. Note that we followed the same steps as in these websites to handle negative book value of equity (in the BE/ME calculations) and any other Compustat data issues.} ``ISS later'' measures the percentage of firms that announced an equity issue within 48 months after the buyback announcement. Next, we measure the percentage of buybacks financed with cash (CASH) when the data is available\footnote{As this SDC data was not available for many events, we did not consider the in the U-index calculation.} (this data was available only for \Sexpr{sum(!(BUYBACK_DATA$DATASET$SDC$Source...of..Funds..Code == ""))} of the events) and whether the reported purpose (available only for \Sexpr{sum(!(BUYBACK_DATA$DATASET$SDC$Purpose.Code == ""))} events) included the term ``Undervalued'', or ``Enhance Shareholder Value'' or ``stock option plan''.

@@

@@

@@

@@

label = "tbl:PastFindingsTimeBB",
bigtitleontop=T,
titleontop=T,
metric1 = "CAR", metric2 = "AR",
scale=1,
lastSpecial=T,
dorotate=T
)
@

@@

@@

@@

EU_relations <- EU_relations[-which(rownames(EU_relations) %in% c("Missed EPS","Beat EPS")),]
rownames(EU_relations)[1] <- "Low Leverage"
rownames(EU_relations)[2] <- "High Leverage"
latex_render_data_frame(
  round(EU_relations,1), 
  title = "EU relations with Firm Characteristics",
  caption="Firm characteristics for each of the 7 EU-index samples. Percentages indicated for all but the last 3 rows, and averages for the last 3 rows. We consider firm \\textit{leverage}, based on data the year before announcement, defined as the ratio $debt/(debt+equity)$. \\textit{ISS later} measures the percentage of firms that announced an equity issue within 48 months after the buyback announcement. Next, we measure the percentage of buybacks financed with cash (\\textit{CASH}) when the data is available and whether the reported purpose included the term \\textit{Undervalued},  \\textit{Enhance Shareholder Value} or \\textit{stock option plan}. Market Cap. is in millions, BE/ME Score is from 1, for firms below the $4^{th}$ Fama-French BE/ME breakpoint, to 5 for firms above the $16^{th}$. Percentage Shares is the percentage shares authorized at announcement.",
  label = "tbl:EUrelations",
  columns=NULL,
  bigtitleontop = T,
  show_rownames=TRUE,
  scale = 1,
  digits=1,
  lastSpecial=F,dorotate=F
)
@

@@

@@
